\bf Eye Fitting Straight Lines in the Modern Era

### 2022-10-06 Eye-Fitting-Straight-Lines-in-the-Modern-Era.Rmd
updated supplementary-material to follow the email guidelines: "You should provide an archive (.zip or .tar) that contains exactly the files listed under supplementary materials. Each item listed should include (1) a title, (2) a brief description, and (3) in parentheses, the file name and file type separated by a comma."

<!-- + **Study Applet:** The shiny app used to conduct the study can be accessed at  [https://emily-robinson.shinyapps.io/you-draw-it-validation-applet/](https://emily-robinson.shinyapps.io/you-draw-it-validation-applet/). -->
<!-- + **RShiny Applet Code:** The code used to create the RShiny Applet for data collection can be found at [https://github.com/earobinson95/you-draw-it-validation-applet(https://github.com/earobinson95/you-draw-it-validation-applet). -->
+ **Participant Data:** De-identified participant data collected in the study and used for analyses are available in `eyefitting-model-data.csv` or may be downloaded from GitHub at  [https://github.com/earobinson95/Eye-Fitting-Straight-Lines-in-the-Modern-Era/tree/main/data](https://github.com/earobinson95/Eye-Fitting-Straight-Lines-in-the-Modern-Era/tree/main/data). 
+ **Data Analysis Code:** The code used to replicate the analysis in this paper can be in `you-draw-it-eyefitting-analysis.Rmd` or found at [https://earobinson95.github.io/Eye-Fitting-Straight-Lines-in-the-Modern-Era/analysis/you-draw-it-eyefitting-analysis.html](https://earobinson95.github.io/Eye-Fitting-Straight-Lines-in-the-Modern-Era/analysis/you-draw-it-eyefitting-analysis.html).

>>>>

<!-- + **Study Applet:** The shiny app used to conduct the study can be accessed at  [https://emily-robinson.shinyapps.io/you-draw-it-validation-applet/](https://emily-robinson.shinyapps.io/you-draw-it-validation-applet/). -->
<!-- + **RShiny Applet Code:** The code used to create the RShiny Applet for data collection can be found at [https://github.com/earobinson95/you-draw-it-validation-applet(https://github.com/earobinson95/you-draw-it-validation-applet). -->
+ **Participant Data:** De-identified participant data collected in the study and used for analyses (eyefitting-model-data.csv).
<!-- `eyefitting-model-data.csv` or may be downloaded from GitHub at  [https://github.com/earobinson95/Eye-Fitting-Straight-Lines-in-the-Modern-Era/tree/main/data](https://github.com/earobinson95/Eye-Fitting-Straight-Lines-in-the-Modern-Era/tree/main/data).  -->
+ **Data Analysis Code:** The code used to replicate the analysis in this paper (you-draw-it-eyefitting-analysis.Rmd).
<!-- or found at [https://github.com/earobinson95/Eye-Fitting-Straight-Lines-in-the-Modern-Era/tree/main/analysis/you-draw-it-eyefitting-analysis.Rmd](https://github.com/earobinson95/Eye-Fitting-Straight-Lines-in-the-Modern-Era/tree/main/supplementary-materials/you-draw-it-eyefitting-analysis.Rmd). -->
+ **README:** File containing detailed descriptions of the supplementary material (README.html).

### 2022-10-06 Eye-Fitting-Straight-Lines-in-the-Modern-Era.tex
updated supplementary-material to follow the email guidelines: "You should provide an archive (.zip or .tar) that contains exactly the files listed under supplementary materials. Each item listed should include (1) a title, (2) a brief description, and (3) in parentheses, the file name and file type separated by a comma."

\begin{itemize}
\tightlist
\item
  \textbf{Participant Data:} De-identified participant data collected in
  the study and used for analyses are available in
  \texttt{eyefitting-model-data.csv} or may be downloaded from GitHub at
  \url{https://github.com/earobinson95/Eye-Fitting-Straight-Lines-in-the-Modern-Era/tree/main/data}.
\item
  \textbf{Data Analysis Code:} The code used to replicate the analysis
  in this paper can be in \texttt{you-draw-it-eyefitting-analysis.Rmd}
  or found at
  \url{https://earobinson95.github.io/Eye-Fitting-Straight-Lines-in-the-Modern-Era/analysis/you-draw-it-eyefitting-analysis.html}.
\end{itemize}

>>>>

\begin{itemize}
\tightlist
\item
  \textbf{Participant Data:} De-identified participant data collected in
  the study and used for analyses (eyefitting-model-data.csv).
\item
  \textbf{Data Analysis Code:} The code used to replicate the analysis
  in this paper (you-draw-it-eyefitting-analysis.Rmd).
\item
  \textbf{README:} File containing detailed descriptions of the
  supplementary material (README.html).
\end{itemize}
